\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-09 related-work.tex
back to 20 pages
Some remarks on first class/second class

There exist many approaches to modular mechanization or proof reuse,
with different focuses and trade-offs.

@@

\noindentparagraph{Solutions to the expression problem} abound.
Our approach is the first that applies family polymorphism~\cite{ernst2001family},
an idea found in the context of OO programming,
to the context of mechanized proofs.
Families in \Lang are second-class, in that they are not considered
terms by themselves.
Families as modeled in \TT (namely linkages) are first-class and thus more flexible.
The distinction corresponds to class-based vs.\ object-base family
polymorphism as summarized before~\cite{cdnw07-tribe}.

>>>>

Approaches to modular mechanization or proof reuse exist,
with different focuses and trade-offs.

@@

\noindentparagraph{Solutions to the expression problem} abound.
Our approach is the first that applies family polymorphism~\cite{ernst2001family},
an idea found in the context of OO programming,
to the context of mechanized proofs.
Families in \Lang are second-class, in that they are not considered
terms by themselves.
Families as modeled in \TT (namely linkages) are first-class and thus more flexible.\EDJ{A more unified way is to consider Coq's Family (our surface syntax) second class corresponds to Inheritance Judgement/Linkage Transformer (secondclass in type theory). Linkage transformer is the helper function to construct first class linkage easily. Even non-derived (surface syntax) family can be considered in this way because they are just inheritance on empty family.}
The distinction corresponds to class-based vs.\ object-base family
polymorphism as summarized before~\cite{cdnw07-tribe}.
